\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-30 Report/project_report.tex
Added rmse and nees table

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONCLUSIONS} \label{sec:conclusions}
Based on our experimental results, we conclude that neither the SWF nor the MSCKF is more effective than pure IMU integration in environments with few features.
In environments with more features, both algorithms provide substantial gains over pure IMU integration, although the SWF significantly outperformed the MSCKF on the datasets we tested.
However, the accuracy of the MSCKF improves as more features are added, while the SWF is less sensitive to feature quantity.
It is unclear from these results which algorithm would perform best in the limit of infinite features.

>>>>

\begin{table*}[t]
  \centering
    \caption{Comparison of root mean squared error (RMSE) and Normalized Estimation Error Squared (NEES) of the MSCKF and SWF for three different synthetic maps generated based on the IMU data in the dataset interval $k\in[1215,1715]$.}
  \begin{tabular}{*{7}{c}}
    \hline
Feature Count & MSCKF Position RMSE & MSCKF Rotation RMSE & MSCKF NEES & SWF Position RMSE & SWF Rotation RMSE & SWF NEES \\ \hline
40            & 0.2672              & 0.1378              & 10.179     & 0.1750            & 0.0495            & 2280     \\
60            & 0.2550              & 0.1247              & 12.03      & 0.1687            & 0.0377            & 2093     \\
100           & 0.2304              & 0.0952              & 16.755     & 0.1755            & 0.0481            & 2013     \\ \hline
  \end{tabular}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{CONCLUSIONS} \label{sec:conclusions}
Based on our experimental results, we conclude that neither the SWF nor the MSCKF is more effective than pure IMU integration in environments with few features.
In environments with more features, both algorithms provide substantial gains over pure IMU integration, although the SWF significantly outperformed the MSCKF on the datasets we tested.
However, the accuracy of the MSCKF improves as more features are added, while the SWF is less sensitive to feature quantity.
It is unclear from these results which algorithm would perform best in the limit of infinite features.
